The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-15 SI.tex
Move 2D-3D graph to SI

The following types materials are chosen for comparison:
\begin{itemize}
\item Bulk covalent materials.  \\
  The list of materials and bandgap are chosen according to
  Ref. \citenum{sze_appendix_2006}, including IV-IV, III-V, II-VI, and
  IV-VI semiconductors. All these materials have isotropic dielectric
  properties.
\item Planar OSc \\
  The planar OScs include metal phthanocyanines, disk-like polycyclic
  aromatic hydrocarbon (PAHs), and benzene derivatives. The
  dimensionality of these materials are close to 2D materials due to
  their planar shape. The bandgap values (mostly at B3LYP density
  functional with 6-31G** basis sets) are extracted from the NIST
  Computational Chemistry Comparison and Benchmark Database
  (http://cccdb.nist.gov, Release 19, April 2018) and the
  polarizability values are obtained from
  Refs. \citenum{Miller_1990,Ramprasad_2006}.
\item Carbon nanotubes (CNT) \\
  Like 2D materials, CNTs are periodic along the 1D directions, and
  shoudl be treated in a similar way to get the polarizability
  proportional to [Length]$^{2}$ \cite{Benedict_1995}. Semiconducting
  zigzag and armchair CNTs are considered, with their electronic
  properties obtained from Refs
  \citenum{Benedict_1995,Matsuda_2010}. and dielectric properties
  obtained from
  Refs. \citenum{Benedict_1995,Jensen_2000,Brothers_2008}.
\item Linear OSc \\
  We choose the polyacenes (linear PAHs from benznene to nonacene) as
  a model system of linear OScs. The bandgaps are obtained from
  \citenum{Salzner_1998} and the polarizabilities are obtained from
  \citenum{Hinchliffe_2005}.
\item Fullerenes \\
  The bandgap of fullerens (C$_{n}$ where $n=60*m^{2}$ where
  $m=1\sim{}7$) are taken from \citenum{Lin_1994} and the
  polarizabilities are taken from \citenum{Martin_2008}. All these
  materials have isotropic polarizability due to the high symmetry.
\end{itemize}

@@

\section{}

\section{Raw data from first principles calculations}
\subsection{Quantities from first principles calculation}
\label{sec:raw}

\input{raw_data}

>>>>

The following types materials are chosen for comparison:
\begin{itemize}
\item Bulk covalent materials.  \\
  The list of materials and bandgap are chosen according to
  Ref. \citenum{sze_appendix_2006}, including IV-IV, III-V, II-VI, and
  IV-VI semiconductors. All these materials have isotropic dielectric
  properties.
\item Planar OSc \\
  The planar OScs include metal phthanocyanines, disk-like polycyclic
  aromatic hydrocarbon (PAHs), and benzene derivatives. The
  dimensionality of these materials are close to 2D materials due to
  their planar shape. The bandgap values (mostly at B3LYP density
  functional with 6-31G** basis sets) are extracted from the NIST
  Computational Chemistry Comparison and Benchmark Database
  (http://cccdb.nist.gov, Release 19, April 2018) and the
  polarizability values are obtained from
  Refs. \citenum{Miller_1990,Ramprasad_2006}.
\item Carbon nanotubes (CNT) \\
  Like 2D materials, CNTs are periodic along the 1D directions, and
  shoudl be treated in a similar way to get the polarizability
  proportional to [Length]$^{2}$ \cite{Benedict_1995}. Semiconducting
  zigzag and armchair CNTs are considered, with their electronic
  properties obtained from Refs
  \citenum{Benedict_1995,Matsuda_2010}. and dielectric properties
  obtained from
  Refs. \citenum{Benedict_1995,Jensen_2000,Brothers_2008}.
\item Linear OSc \\
  We choose the linear polyacenes (linear PAHs from benznene to
  nonacene) and zigzag polyacetylene (1--9 repeating units) as model
  systems of linear OScs. The bandgaps are obtained from
  \citenum{Salzner_1998} and the polarizabilities are obtained from
  \citenum{Hinchliffe_2005}.
\item Fullerenes \\
  The bandgap of fullerens (C$_{n}$ where $n=60*m^{2}$ where
  $m=1\sim{}7$) are taken from \citenum{Lin_1994} and the
  polarizabilities are taken from \citenum{Martin_2008}. All these
  materials have isotropic polarizability due to the high symmetry.
\end{itemize}

@@

\subsection{The relation between 2D and 3D physical quantities}
As schematically shown in Figure \ref{fig-2D-3D}, the physical
quantities related to the dielectric properties can be categorized
into (i) strictly 2D (microscopic), (ii) strictly 3D (macroscopic) and
(iii) valid both 2D and 3D.  $\alpha_{\mathrm{2D}}$ and $\varepsilon$ are the
starting point for the strictly 2D and 3D quantities, which require
distinct definitions when dimensionality changes. Such quantities
include (but not limited to):
\begin{enumerate}
\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
  charge, polarization, electronic states, etc.

\item The plasma frequencies $\omega^{\mathrm{p}}_{\mathrm{2D}}$ and
  $\omega^{\mathrm{p}}_{\mathrm{2D}}$\cite{Nazarov_2015_2D_3D} (see
  Section \ref{ssec:omega-p} and Figure \ref{fig:plasma}).

\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
\end{enumerate}
These quantities have distinct units in both dimensions, and related
by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
plasma frequency), which requires prudent interpretation of
theoretical and experimental results. For instance, the experimentally
observed ``dielectric constant'' of monolayer 2D materials
\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
without considering the effect of mix ted medium. Instead, the 2D slab
polarizability, either transformed from the vacuum-containing
macroscopic dielectric constant, or predicted from the bandgap and
geometry as proposed here, will be a better descriptor for the true 2D
dielectric nature. On the other hand, there are also
dimension-independent quantities that valid for both 2D and 3D
systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
as well as the Hamaker constant of van der Waals interaction
$A_{\mathrm{H}}$. All these quantities are well-defined and can be
measured in both dimensions, while their relation with the dielectric
property varies with dimensionality. The well-known examples are the
different Wannier-Mott laws for exciton binding energy
\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
proposed here, and the distinct power laws for van der Waals
interactions \cite{Gobre_2013}. To get a accuracy description of
dielectric-related properties of the 2D materials and their
heterostructures, one has to distinguish between the 2D and 3D
properties, and choose a suitable relation with the
dimension-dependent and dimension-independent quantities.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\linewidth]{img/fig-2D-vs-3D.pdf}
\caption{\label{fig-2D-3D} Dielectric-related physical quantities in
  both 2D (red circle) and 3D (cyan circle) systems. The
  dimension-dependent quantities can be related with $\alpha_{\mathrm{2D}}$ and
  $\varepsilon$, respectively. The intersection between the circles
  present the quantities are well-defined in both dimensions, but may have a
  different scaling relation with others quantities.}
\end{figure}

\section{Raw data from first principles calculations}
\subsection{Quantities from first principles calculation}
\label{sec:raw}
\todo[inline]{I think showing the $\alpha$ values is enough since
  whoever interested in calculating the $r_{0}$ values can simply
  multiply them by $2 \pi$. }
\input{raw_data}

### 2018-11-15 paper.tex
Move 2D-3D graph to SI

\subsection{Implications for Experiments}
\todo[inline]{Wait for comments from JC and MC.}
\iffalse
Finally, we would like to comment on the implications of this work for
the experiments concerning the dielectric properties of 2D materials.
As schematically shown in Figure \ref{fig-2D-3D}, the physical
quantities related to the dielectric properties can be categorized
into (i) strictly 2D (microscopic), (ii) strictly 3D (macroscopic) and
(iii) valid both 2D and 3D.  $\alpha$ and $\varepsilon$ are the
starting point for the strictly 2D and 3D quantities, which require
distinct definitions when dimensionality changes. Such quantities
include (but not limited to):
\begin{enumerate}
\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
  charge, polarization, electronic states, etc.

\item The plasma frequencies $\omega^{\mathrm{p}}_{\mathrm{2D}}$ and
  $\omega^{\mathrm{p}}_{\mathrm{2D}}$\cite{Nazarov_2015_2D_3D} (more
  details see Supplementary Section S4.4).

\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
\end{enumerate}
These quantities have distinct units in both dimensions, and related
by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
plasma frequency), which requires prudent interpretation of
theoretical and experimental results. For instance, the experimentally
observed ``dielectric constant'' of monolayer 2D materials
\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
without considering the effect of mix ted medium. Instead, the 2D slab
polarizability, either transformed from the vacuum-containing
macroscopic dielectric constant, or predicted from the bandgap and
geometry as proposed here, will be a better descriptor for the true 2D
dielectric nature. On the other hand, there are also
dimension-independent quantities that valid for both 2D and 3D
systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
as well as the Hamaker constant of van der Waals interaction
$A_{\mathrm{H}}$. All these quantities are well-defined and can be
measured in both dimensions, while their relation with the dielectric
property varies with dimensionality. The well-known examples are the
different Wannier-Mott laws for exciton binding energy
\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
proposed here, and the distinct power laws for van der Waals
interactions \cite{Gobre_2013}. To get a accuracy description of
dielectric-related properties of the 2D materials and their
heterostructures, one has to distinguish between the 2D and 3D
properties, and choose a suitable relation with the
dimension-dependent and dimension-independent quantities.
\todo[inline]{I plan to use the original section for the ``implication for experiments''. Please help to add more on this part.}
\fi

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\linewidth]{img/fig-2D-vs-3D.pdf}
\caption{\label{fig-2D-3D} Dielectric-related physical quantities in
  both 2D (red circle) and 3D (cyan circle) systems. The
  dimension-dependent quantities can be related with $\alpha$ and
  $\varepsilon$, respectively. The intersection between the circles
  present the quantities are well-defined in both dimensions, but may have a
  different scaling relation with others quantities.}
\end{figure}
\end{document}

>>>>

\subsection{Implications for Experiments}
\todo[inline]{Wait for comments from JC and MC.}

@@

\end{document}
